---
date: "`r format(Sys.time(), '%d %B, %Y')`"
editor_options: 
  chunk_output_type: console
output: rmarkdown::html_vignette
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(kableExtra)

#library(rgdal)
library(move)
library(dplyr)
library(leaflet)
library(units)
#library(sf)
library(viridis)
library(kableExtra)
library(lubridate)
#library(plotly)
## Load packages for google drive ---- not needed yet
#library(googledrive)
#library(purrr)
#library(readxl)
#options(googledrive_quiet = TRUE)


# Import passcodes
MOVE_PASS <- Sys.getenv("MOVEBANK_PASSWORD")
MOVE_USE <- Sys.getenv("MOVEBANK_USERNAME")

loginStored <- movebankLogin(username=MOVE_USE, 
                             password=MOVE_PASS)
# Get animals
animals <-getMovebankAnimals(study=1573471517,login=loginStored)

# Ocelot
tmp <-getMovebankAnimals(study=2526574641,login=loginStored)

# Tapir
tmp2 <- getMovebankAnimals(study=1954804459,login=loginStored)

# Carnivores
tmp3 <- getMovebankAnimals(study=2957292408,login=loginStored)


animals <- rbind(animals, tmp,tmp2, tmp3)



# For some reason they are duplicated
animals[duplicated(animals)==F,]
# They vary by the field "sensor_type_id"
animals <- animals[animals$sensor_type_id==653 & is.na(animals$sensor_type_id)==F,]

# Get last 2 weeks
t <- now("America/Costa_Rica")
start_t <- t-as.difftime(14,units='days')
start_tapir <- t-as.difftime(48,units='days')


mov_dat <- getMovebankData(study=1573471517, login=loginStored,  removeDuplicatedTimestamps=TRUE,
                       timestamp_start=start_t)

#Ocelot - REMOVED AS PROJECT IS DONE
#tmp <- getMovebankData(study=2526574641, login=loginStored,  removeDuplicatedTimestamps=TRUE)

#Tapir
tmp2 <- getMovebankData(study=1954804459, login=loginStored,  removeDuplicatedTimestamps=TRUE,
                       timestamp_start=start_tapir)

# Carnivores
tmp3 <- getMovebankData(study=2957292408, login=loginStored,  removeDuplicatedTimestamps=TRUE,
                       timestamp_start=start_tapir)


mov_dat <- moveStack(mov_dat, tmp2, tmp3)
# Add distance moved
mov_dat$distance <- unlist(lapply(distance(mov_dat), c, NA))
# all data
#dat <- getMovebankData(study=1573471517, login=loginStored,  removeDuplicatedTimestamps=TRUE)

# Convert move stack to dataframe
dat <- as.data.frame(mov_dat)

# Last 24 hours
mov_dat_24 <- mov_dat[mov_dat$timestamp > t-as.difftime(1,units='days'),]
dat_24 <- as.data.frame(mov_dat_24)
table(dat_24$local_identifier)

dist_24<- distance(mov_dat_24)
dist_24<- as.data.frame((sapply(dist_24,sum)))
dist_24$name <- row.names(dist_24)
colnames(dist_24)[1] <- "dist_km_last_24h"
dist_24$dist_km_last_24h <- round(dist_24$dist_km_last_24h/1000,1)
dist_24$name[dist_24$name=="Robin.Hood"] <- "Robin Hood"

# Last 72 hours
mov_dat_72 <- mov_dat[mov_dat$timestamp > t-as.difftime(3,units='days'),]
dat_72 <- as.data.frame(mov_dat_72)
tmp <- as.data.frame(table(dat_72$local_identifier))

dist_72<- distance(mov_dat_72)
dist_72<- as.data.frame((sapply(dist_72,sum)))
dist_72$name <- row.names(dist_72)
colnames(dist_72)[1] <- "dist_km_last_72h"
dist_72$dist_km_last_72h <- round(dist_72$dist_km_last_72h/1000,1)
# Filte rout individuals with only one record
dist_72 <- dist_72[dist_72$name %in% tmp$Var1[tmp$Freq>10],]

# Convert dat to costa rica time
dat$timestamp <- with_tz(dat$timestamp, tzone = "America/Costa_Rica")

# Add the location data
dat <- left_join(dat, animals[, c("tag_id", "animalName")])
# Sort the names out

dat$animalName <- sub('\\_.*', '', dat$animalName)
# Add in the taxonomic group
dat$animalName <- paste0(dat$animalName, "_", sub('\\ .*', '', dat$taxon_canonical_name))
animals$animalName <- paste0(sub('\\_.*', '', animals$animalName), "_", sub('\\ .*', '', animals$taxon_canonical_name))

animals$timestamp_start <- ymd_hms(animals$timestamp_start)
animals$timestamp_end <- ymd_hms(animals$timestamp_end)



# Add a country column
dat$country <- dat$location_lat<0
dat$country[dat$country==T] <- "peru"
dat$country[dat$country==F] <- "costa_rica"
#table(dat$country)

# What speed is flying

# Last location and time since present
dat$diff_time <- round(as.numeric(difftime(t, dat$timestamp, units="hours")),1)

last_obs <- dat %>% group_by(animalName) %>% summarize(hours_since_fix=min(diff_time))

last_dat <- dat %>% group_by(animalName) %>% filter(row_number()==n())

last_sum  <- dat %>% 
  group_by(local_identifier) %>%
  slice(which.max(timestamp))
last_sum$behaviour <- NA
last_sum$behaviour[last_sum$ground_speed>5 & is.na(last_sum$ground_speed)==F] <- "flying"
last_sum$behaviour[last_sum$ground_speed<5 & is.na(last_sum$ground_speed)==F] <- "roosting"

tmp <- last_sum[, c("local_identifier","taxon_canonical_name","country", "timestamp", "diff_time", "behaviour")]
tmp <- left_join(tmp, last_dat[, c("local_identifier", "eobs_battery_voltage")])

colnames(tmp)[colnames(tmp)=="local_identifier"] <- "name"
colnames(tmp)[colnames(tmp)=="diff_time"] <- "time_since_checkin_h"
colnames(tmp)[colnames(tmp)=="timestamp"] <- "last_timestamp"
colnames(tmp)[colnames(tmp)=="eobs_battery_voltage"] <- "last_battery_level"

check_in_summary <- tmp[order(tmp$country, tmp$time_since_checkin_h),]

# add distance move last_24
check_in_summary <- left_join(check_in_summary, dist_24)

### Add additional data shown later
check_in_summary$duration <- difftime(check_in_summary$last_timestamp, start_t, "days")

### Total locations Mean eobs battery power, eobs accuracy
tmp_sum <- dat %>% group_by(local_identifier) %>% summarise(total_obs=n(), mean_batt=mean(eobs_battery_voltage, na.rm=T), loc_accuracy=mean(eobs_horizontal_accuracy_estimate, na.rm=T))
colnames(tmp_sum)[1] <- "name"

check_in_summary <- left_join(check_in_summary, tmp_sum)
check_in_summary$mean_locs_per_day <- round(check_in_summary$total_obs/as.numeric(check_in_summary$duration),0)

#### Tags to be checked


warnings <- list()
check_in_concern <- list()
counter <- 1
# Tags which have haven't checked in > 8 days, OR maximum distance moved between intervals < 100m for the last 100 fixes or total distance moved in last 100 fixes <5000m
tmp_check  <- check_in_summary[check_in_summary$time_since_checkin_h>(96*2) & is.na(check_in_summary$dist_km_last_24h)==T,]$name

if(length(tmp_check)>0)
{
  check_in_concern[[1]] <- data.frame(name=tmp_check,reason="Last checkin > 8 days ago")
 
}

tmp2 <- dat %>% 
   group_by(local_identifier) %>% 
   slice(tail(row_number(), 100))
test <- tmp2[tmp2$local_identifier=="Ugalde",]
tmp3 <- tmp2 %>% group_by(local_identifier) %>% summarize("max_distance"=max(distance, na.rm=T), "avg_distance"=mean(distance, na.rm=T), "distance"=sum(distance, na.rm=T))

tmp_check <- tmp3[tmp3$max_distance<100,]$local_identifier
if(length(tmp_check)>0)
{
  warnings[[counter]] <- data.frame(name=tmp_check,reason="Maximum movement step < 100m")
  counter <- counter+1
}

tmp_check <- tmp3[tmp3$distance<5000,]$local_identifier

if(length(tmp_check)>0)
{
  warnings[[counter]] <- data.frame(name=tmp_check,reason="Avg. movement step < 50m")
  counter <- counter+1
}

warnings <- bind_rows(warnings)
check_in_concern <- bind_rows(check_in_concern)

```

**DEATH ALERTS**
The following list shows tags which have hit one of two criteria:

In the last 100 locations the maximum movement step is below 100m OR the average movement steps is below 50 m: 

`r if(nrow(warnings)>0){warnings %>% kbl() %>%  kable_styling() %>% column_spec(1:2, background = "#ff7777")}else{print("All tags functioning")}`
<<<<<<< HEAD
 
=======

>>>>>>> 9c662e6c98fdc4329bdc60b482985eb1debe0344
**Check-in warning**
The following tags have not checked in for >8 days (which may be a sign of an issue):

`r if(nrow(check_in_concern)>0){check_in_concern %>% kbl() %>%  kable_styling() %>% column_spec(1:2, background = "#ff772250")}else{print("All tags functioning")}`

**Tag summaries**

Here is your automated summary of all the tracked animals which have checked in within the last 14 days:

```{r cars, echo=F}
tmp_col <- check_in_summary$time_since_checkin_h
tmp_col[tmp_col<12]<- 12

tmp_col3 <- check_in_summary$dist_km_last_24h
# what to do with NA;s
tmp_col3[is.na(tmp_col3)] <- 100 

check_in_summary[,c("name","taxon_canonical_name","country","time_since_checkin_h","behaviour","dist_km_last_24h","mean_locs_per_day", "last_battery_level" )] %>%
  kbl() %>%
  kable_styling() %>% 
  column_spec (1:7,border_left = F, border_right = T) %>%
  column_spec(4, color = "white",
              background = spec_color(tmp_col, begin=0,end = 0.7, scale_from = c(12,72), direction=-1)) %>% 
  column_spec(6, background = ifelse(tmp_col3>0.5, "white", "#fec44f")) %>% 
  column_spec(8, background = ifelse(tmp_col3<3600, "white", "#fec44f"))

```

*Note* For the behavior column - we use ground speed >5 m/s to indicate that the bird was likely flying. Mammals automatically get NA. 

For the current locations of all animals see: [Osa Conservation Daily Report](https://chrisbeirne.github.io/Osa-Conservation-Movement-Ecology-Daily-Report/)

Tagged animals which have not checked in for >14 days:

```{r  c05, echo=F}
tmp2 <- animals[!(animals$local_identifier %in% tmp$name),]
tmp2$timestamp_end <- with_tz(tmp2$timestamp_end, tzone = "America/Costa_Rica")
#str(tmp2)
tmp2$days_since_check_in<- round(as.numeric(difftime(t, tmp2$timestamp_end, units="days")),1)
tmp2 <- tmp2[order(tmp2$days_since_check_in),]
#row.names(tmp2) <- 1:nrow(tmp2)
colnames(tmp2)[colnames(tmp2)=="local_identifier"] <- "name"

tmp2[, c("name", "timestamp_end", "days_since_check_in")] %>%
  kbl(row.names = FALSE) %>%
  kable_styling() %>% 
  column_spec (1:3,border_left = F, border_right = T) 

```

For the current locations of all animals see: [Osa Conservation Daily Report](https://chrisbeirne.github.io/Osa-Conservation-Movement-Ecology-Daily-Report/)
